---
title: "Case Studies (2017, 2023, 2024)"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

Code results in 'output/case_studies_all_data_2026-01-02.csv' 

## Load BANTER scores
```{r}
scores <- read_csv(here('output', 'AllSignals_CaseStudies_20251217.csv')) #saved in BANTER_Predict, Signal_Counts.rmd

scores$event.id <- as.character(scores$event.id)

```

## Load Detection Logs
```{r}

scope1 <- read.csv('C:\\Users\\yvonne.barkley\\Github\\ClassyPc\\data\\detection_logs\\2024_SCOPE_2404_log1.csv')

scope2 <- read.csv('C:\\Users\\yvonne.barkley\\Github\\ClassyPc\\data\\detection_logs\\2024_SCOPE_2404_log2.csv')

scope3 <- read.csv('C:\\Users\\yvonne.barkley\\Github\\ClassyPc\\data\\detection_logs\\2024_SCOPE_2404_log3.csv')
scope2024log <- rbind(scope1, scope2, scope3) %>% arrange(ac_id) %>% 
    rename(lat = latlong_LAT, lon = latlong_LON) %>% 
  select(-c(1:8,15:31, 33,34, 36,37:40)) %>% 
  mutate(date_time_start = ymd_hms(date_time_start),
         date_time_end = ymd_hms(date_time_end),
         ship = 2404,
         year = 2024,
         event.id = paste0(ship, str_pad(ac_id, width = 3, pad = "0")))
colnames(scope2024log)

## HICEAS 2017 log
hiceas2017 <- read.csv('C:\\Users\\yvonne.barkley\\Github\\ClassyPc\\data\\detection_logs\\2017_HICEAS.csv')
colnames(hiceas2017)

hiceas2017log <- rename(hiceas2017, ship = cruiseID,
                        lat = latitude, lon = longitude) %>%
  arrange(ac_id) %>%
  select(-c(2:7,14:30,32,33,35:41 )) %>% 
  mutate(date_time_start = mdy_hm(date_time_start),
         date_time_end = mdy_hm(date_time_end), year = 2017,
         event.id = paste0(ship, str_pad(ac_id, width = 3, pad = "0")))
# hiceas2017log$ship <- as.character(hiceas2017log$ship)


hiceas2303 <- read.csv('C:\\Users\\yvonne.barkley\\Github\\ClassyPc\\data\\detection_logs\\2023_HICEAS_2303.csv')
hiceas2303$ship <- 2303
hiceas2303$vis_id <- as.numeric(hiceas2303$vis_id)
hiceas2303$vis_id <- ifelse(is.na(hiceas2303$vis_id), 97, hiceas2303$vis_id)

hiceas2401 <- read.csv('C:\\Users\\yvonne.barkley\\Github\\ClassyPc\\data\\detection_logs\\2023_HICEAS_2401.csv')
hiceas2401$ship <- 2401

hiceas2023log <- rbind(hiceas2303, hiceas2401) %>% 
  rename(lat = latlong_LAT, lon = latlong_LON) %>%
  mutate(date_time_start = mdy_hms(StartTime),
         date_time_end = mdy_hms(EndTime),
         year=2023,
         event.id = paste0(ship, str_pad(ac_id, width = 3, pad = "0"))) %>% 
  arrange(ac_id) %>% select(-c(1:9,12:14,19:35,37:38,40:45)) 

   
case_study_log <- bind_rows(scope2024log, hiceas2017log, hiceas2023log)
# case_study_log$event.id <- as.numeric(case_study_log$event.id)

write.csv(case_study_log, here('data', 'case_studies_detlog_.csv'))

```


## Join scores/counts with log by event.id
```{r}

event_data <- inner_join(scores, case_study_log, by= 'event.id') 

# Add columns for sightings and whether or not Pc
event_data$vis_ver <- ifelse(event_data$vis_id <999, 1, 0)
event_data$pc <- ifelse(event_data$VVAO==2 | event_data$VVAO==1, 1, 0)
# Removing extra year column
event_data <- event_data %>% select(-c(12)) %>% 
  rename(year=year.y)

write.csv(event_data, here('output', 'case_studies_scores_detlog.csv'), row.names = FALSE)

```


## Load Case Study AcStudies for Event Summ
Get the 'keep' columns from the event summary tables
```{r}
#Use acoustic studies filtered for noise already
#1706
detsFilt <- readRDS("C:\\Users\\yvonne.barkley\\Github\\ClassyPc\\data\\Acoustic_Studies/2017_HICEAS_1706_ch5w32s_F.rds")
#1705
detsFilt <- readRDS("C:\\Users\\yvonne.barkley\\Github\\ClassyPc\\data\\Acoustic_Studies/2017_HICEAS_1705_ch5_F.rdata")
#2303
detsFilt <- readRDS("C:\\Users\\yvonne.barkley\\Github\\ClassyPc\\data\\Acoustic_Studies/2023_HICEAS_2303_ch5_F.rdata")
#2401
detsFilt <- readRDS("C:\\Users\\yvonne.barkley\\Github\\ClassyPc\\data\\Acoustic_Studies/2023_HICEAS_2401_ch5_F.rdata")
#2404
detsFilt <- readRDS("C:\\Users\\yvonne.barkley\\Github\\ClassyPc\\data\\Acoustic_Studies/2024_SCOPE_2404_ch5_F.rdata")

```

## Event Table w/ MDF & SSF 
```{r}
# set up output data frame
nEventsFilt <- length(names(events(detsFilt)))
evTable <- data.frame(eventId = character(nEventsFilt)) #, 
evTable$eventId <- names(PAMpal::events(detsFilt))

# get all click data
allClicks <- getClickData(detsFilt)
# pull click summary stats
evClickSummary <- allClicks %>%
  group_by(eventId) %>%
  summarise(
    numClicks = n(),
    # numClicks_d0 = sum(detectorName == 'Click_Detector_0', na.rm = TRUE),
    numClicks_d1 = sum(detectorName == 'Click_Detector_1', na.rm = TRUE),
    numClicks_d2 = sum(detectorName == 'Click_Detector_2', na.rm = TRUE),
    numClicks_d3 = sum(detectorName == 'Click_Detector_3', na.rm = TRUE),
    numClicks_d4 = sum(detectorName == 'Click_Detector_4', na.rm = TRUE),
    numClicks_d5 = sum(detectorName == 'Click_Detector_5', na.rm = TRUE),
    click_medPeakFreq_kHz = median(peak, na.rm = TRUE), 
    click_p25PeakFreq_kHz = quantile(peak, 0.25, na.rm = TRUE), 
    click_p75PeakFreq_kHz = quantile(peak, 0.75, na.rm = TRUE)
  )
# add to output evTable
evTable <- evTable %>%
  left_join(evClickSummary, by = c('eventId' = 'eventId'))

# get all whistle data
allWhistles <- getWhistleData(detsFilt)
# pull whistle summary stats
evWhistleSummary <- allWhistles %>%
  group_by(eventId) %>%
  summarise(
    numWhistles = n(),
    # whistle_medCenterFreq_Hz = median(freqCenter, na.rm = TRUE),
    # whistle_medMedFreq_Hz = median(freqMedian, na.rm = TRUE),
    whistle_medBeginFreq_Hz = median(freqBeg, na.rm = TRUE),
    whistle_percBeginFreq4to8kHz = sum(freqBeg >= 4000 & freqBeg <= 8000)/n()
    # whistle_percCenterFreq5to7kHz = sum(freqCenter >= 5000 & freqCenter <= 7000)/n(),
    # whistle_percMedianFreq5to7kHz = sum(freqMedian >= 5000 & freqMedian <= 7000)/n()
  )
# add to output evTable
evTable <- evTable %>%
  left_join(evWhistleSummary, by = c('eventId' = 'eventId'))

# MDF & SSF
evTable$keep <- FALSE # set all to false, will mark keepers as TRUE in loop
# mark true where events meet criteria
evTable$keep[which(# evTable$numClicks >= 10 &
  (evTable$numClicks_d1 >= 20 |
     evTable$numClicks_d2 >= 20 |
     evTable$numClicks_d3 >= 20 |
     evTable$numClicks_d4 >= 20 |
     evTable$numClicks_d5 >= 20 |
     evTable$numWhistles >= 20) &
    (is.na(evTable$numClicks) | # if there are clicks check for freq criteria
       evTable$click_medPeakFreq_kHz <= 22) &
    (is.na(evTable$numWhistles) | # if there are whistles, check for freq criteria
       evTable$whistle_medBeginFreq_Hz <= 8100 &
       evTable$whistle_percBeginFreq4to8kHz >= .5))] <- TRUE

# MDF only
evTable$keepMDF <- FALSE
evTable$keepMDF[which(# evTable$numClicks >= 10 &
  (evTable$numClicks_d1 >= 20 |
     evTable$numClicks_d2 >= 20 |
     evTable$numClicks_d3 >= 20 |
     evTable$numClicks_d4 >= 20 |
     evTable$numClicks_d5 >= 20 |
     evTable$numWhistles >= 20))] <- TRUE


# SSF only
evTable$keepSSF <- FALSE
evTable$keepSSF[which(# evTable$numClicks >= 10 &
  ((is.na(evTable$numClicks) | # if there are clicks check for freq criteria
       evTable$click_medPeakFreq_kHz <= 22) &
    (is.na(evTable$numWhistles) | # if there are whistles, check for freq criteria
       evTable$whistle_medBeginFreq_Hz <= 8100 &
       evTable$whistle_percBeginFreq4to8kHz >= .5)))] <- TRUE

assign(paste0("evTable_", detsFilt@id), evTable) 

```

## Save Event Tables
```{r}
# Combine evTables for all surveys

evTable_case_study<-rbind(evTable_2017TA_1705,evTable_2017TA_1706,evTable_2023TA_2303,evTable_2023TA_2401,evTable_2024TA_2404) %>% rename(event.id = eventId)


write.csv(evTable_case_study, file = here('output', paste0('case_studies_eventsumm_',
                                                           Sys.Date(),'.csv')))
```


## Join Scores/Log data with Event Table
READ CAREFULLY
Acoustic studies that are filtered for noise to make the event summaries remove certain events from 1705, "1705237" "1705247" "1705343" "1705362" "1705363" for no apparent reason from the acoustic study itself. BANTER predictions were run on noise filtered banter objects, which keep these events. To calculate the correct baseline information, these events need to be included in the dataset, and will eventually get filtered out after in the MDF stage since they all have fewer than 20 sigs and/or >22 kHz click peaks.
YB Manually edited the event table for the missing events to include the number of clicks after being filtered for noise to match the other event summary info, including the TRUE/FALSE for the 3 'keep' columns. YB checked the median peak frequency and only 1705247 passed for SSF, all other events failed for both MDF and SSF.
Intermediate csvs are saved in 'output' folder. Includes, case_studies_banterData_missing1705_2026-01-02.csv, to get noise-filtered banter data for signal totals for the 5 events. 

```{r}
case_study_all <- inner_join(event_data, evTable_case_study, by= 'event.id') 

#Check that all event.id exist - THEY DO NOT for 1705
setdiff(event_data$event.id, evTable_case_study$event.id)

#Load raw acstudy, then ran through event summary steps to pull out data for missing events
detsFilt <- readRDS("C:\\Users\\yvonne.barkley\\Github\\ClassyPc\\data\\Acoustic_Studies/2017_HICEAS_1705_ch5.rdata")

#Filter for just the missing events
evTable_miss <- filter(evTable, eventId %in% c("1705237" ,"1705247" ,"1705343", "1705362", "1705363") )

#export for manual editing - see _YVONNE_ Projects notes
write.csv(evTable_miss, file = here('output', paste0('case_studies_eventsumm_missing1705_',
                                                           Sys.Date(),'.csv')))

# ~~~~~~~~~~~
#import manually edited event summary data for join
evTable_miss_edit <- read.csv(here('output', paste0('case_studies_eventsumm_missing1705_EDIT_',                                                         Sys.Date(),'.csv')))

#Combine edited missing event data with other case study data
evTable_case_study2 <- rbind(evTable_case_study, evTable_miss_edit)

#Join event table summ with banter scores and detection log info 
case_study_all2 <- inner_join(event_data, evTable_case_study2, by= 'event.id') 

#save in output
write.csv(case_study_all2, file = here('output', paste0('case_studies_all_data_',
                                                           Sys.Date(),'.csv')), row.names = F)

```





