---
title: "Minimum Data Filter: Evaluate minimum data to optimize classification performance using combinations of detectors"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

# Prediction Steps

## Load libraries, functions, and set directory

```{r, load packages, message=FALSE}
rm(list=ls())

library("easypackages")
libraries("PAMpal", "tidyverse", "banter", "rfPermute", "manipulate", "here", "caret", "future", "foreach", "doFuture", "progressr")

## functions
source(here('_R_code/filterClicks.r'))

#function to change species Id in banter object
new_sp_id <- function(x, nonPC) {
  for (e in seq_along(x[["events"]][["species"]]) ) {
    if (  x[["events"]][["species"]][[e]] != 33 ) {
      x[["events"]][["species"]][[e]] <- nonPC
    } 
  }
 x 
}

#function to take the log of the signals per detector for plotting purposes
make_log_seq <- function(df, column_name, new_column_name = "Log_Sequence", from = 1, to = length(callsPrd)) {
    unique_vals <- sort(unique(df[[column_name]])) # Get unique values
    log_seq <- log10(callsPrd) # Generate log values of original sequence
  
  # Create a lookup table and map it to the original values
    lookup <- setNames(log_seq, unique_vals) 
    df[[new_column_name]] <- lookup[as.character(df[[column_name]])]
  
  return(df)
}

#change which detectors are included in data to predict on
select_detectors <- function(bant_lst, detector_nums) {

  # Make a copy of the original list
  new_lst <- bant_lst
  
  # Subset detectors
  new_lst$detectors <- bant_lst$detectors[detector_nums]
  
  return(new_lst)
}

#Set time zone to UTC
Sys.setenv(TZ = 'UTC')

here()
```


## Load banter model

Load original model from McCullough et al. 2021.

```{r}
bant_model <- readRDS(file.path('data', "BanterModel_McCullough2021.rds"))
```

## Load and process prediction data
Section 2.2.1
Load visually-verified PAM data in an acoustic study format. Then filter clicks for noise.

```{r}
# acoustic study
acstudy_predict <- readRDS(file.path('data', 'AcStudy_HI_MI_pred.rds') ) 

# filter noise from click data
acstudy_filt <- filterClicks(acstudy_predict)

```

## Species codes to exclude from analysis = unidentified dolphins and beaked whales
Numeric codes come from 'Cetacean species codes.txt' in data folder
```{r}
drop_Sp <- c('77','177','277','377','49','59','61','65')
```


## Choose detector combination

Choose one of the options depending on what detectors are included in the analysis. 

```{r}
# The order of detectors in the banter object can change. That is accounted for in the code. These values are just for informational purposes.

#All Detectors
dets <- c(2:8)
det_code <- 'ALL' #clicks, whistles, cepstrum

#Clicks and Whistles Only
# dets <- c(2:4,6:8)
# det_code <- 'ECDW'

#Clicks and Cepstrum Only
# dets <- c(2:5,7,8)
# det_code <- 'ECCEP'

#Whistles and Cepstrum Only
# dets <- c(5,6)
# det_code <- 'DWCEP'

#Whistles Only
# dets <- c(6)  #YB checked, 7= click_detector4 
# det_code <- 'DW'

#Clicks Only
# dets <- c(2:4,7,8)  #YB checked, 7= click_detector4 
# det_code <- 'EC'

#Burst pulses only
# dets <- 5
# det_code <- 'BP'
```

## Parameters for Predictions

```{r}

#TEST PARAMETERS
# For all detectors
# callsMod <- 'All' # Use all signals 
callsPrd <- c(3, 6, 10, 20, 30, 40, 50, 100, 200, 300, 400, 500, 10000, 20000, 30000) 

iters <- c(1:100)

predxn_params <- list(callsPrd=callsPrd,
                     dets=dets,
                     det_code = det_code,
                     iters=iters,
                     notes = paste0(det_code, ' - Excludes BWs and Unids. - ', Sys.time()) )
                

if (!dir.exists(file.path("output"))) {
  dir.create(file.path("output"))
}

saveRDS(predxn_params, file.path("output", paste0("sens_an_", det_code, "_params.rds")) )

```

## RUN Sensitivity Analysis Loop

```{r}


### START LOOP ####

#save predictions for all iterations of the sensitivity analysis
sens_an_preds_dets <- list()
counter <-1

options(doFuture.rng.onMisuse = "ignore", future.globals.maxSize = 2 * 1024^3)
plan("multisession", workers=4)

tictoc::tic()

for (i in iters){

      # for (call_prd in callsPrd){
    pred_output <- foreach(p = callsPrd,  .options.future = list(packages = c("banter", "randomForest"))) %dofuture% {

    #The variation in results stems from the random selection 
    #of signals from each detector in an encounter.
    acstudy_predict_sub <- sampleDetector(acstudy_filt, n=p)  
    
    # Print Run Info
    cat("***PREDICTIONS***: Iter", i, "For pred calls=", p, "detectors =", dets)
    
    # banter_pred <- export_banter( c(events(acstudy_predict_sub), training=FALSE) )
    banter_pred <- export_banter(acstudy_predict_sub, training=FALSE, dropSpecies = drop_Sp) 
    
    ## Make a dataframe with event IDs and original species codes
    origSpCodes <- data.frame(banter_pred[["events"]])
    
    ## Change 'other' species code to 577
    banter_pred <- new_sp_id(banter_pred, "577")
    
 
   ## Select subset of detectors using correct index
  det_names <- names(banter_pred[["detectors"]])
  click_idx      <- which(grepl("^Click_Detector_", det_names))
  cepstrum_idx  <- which(det_names == "Cepstrum_Detector")
  whistle_idx   <- which(det_names == "Whistle_and_Moan_Detector")
    
  if (det_code == 'ECDW'){
  det_ind <- c(click_idx[2:6], whistle_idx) 
  } else if (det_code == 'ECCEP') {
    det_ind <- c(click_idx[2:6], cepstrum_idx)
  } else {
    det_ind <- c(whistle_idx, cepstrum_idx)
  }
    
   banter_pred_sub <- select_detectors(banter_pred, det_ind)      
    
    ## Apply model, get predictions, make a dataframe to compare true event IDs to predictions
    
    pred_results <- banter::predict(bant_model, banter_pred_sub)
    
    pred_resultsDF <- as.data.frame(pred_results[["predict.df"]])
    
    pred_resultsDF <- pred_resultsDF[, c(1, 5, 2:4,6)]
    
    pred_resultsDF <- inner_join(origSpCodes, pred_resultsDF, by = 'event.id')
    
    pred_resultsDF$iter = i
    pred_resultsDF$tot_sigp = p
    # pred_resultsDF$tot_sigm = callsMod
    pred_resultsDF$dets = paste(dets, collapse = "")
    
    # create different predictions based on higher threshold values
    pred_resultsDF$predicted60 <- "X577"
    for (thd in seq(1:nrow(pred_resultsDF))){
      if (pred_resultsDF$X33[thd] >= 0.6) {
        pred_resultsDF$predicted60[thd] <- "X33"
      }
    }
    

confMat <- caret::confusionMatrix(factor(pred_resultsDF$predicted),
                                  factor(pred_resultsDF$original), 
                                  mode = 'everything', 
                                  positive = 'X33')

 return(list(
   pred_results = pred_resultsDF, 
   confmat_score = confMat))

 } # callsPrd
    
 ## save prediction results
    sens_an_preds_dets[[counter]] <- pred_output
     counter <- counter + 1 
    
  } #iteration
# )
plan("sequential")

tictoc::toc()

## Save predictions from sensitivity analysis
saveRDS(sens_an_preds_dets, file= file.path('output', paste0('sens_an_', det_code, '_results.rds') ) )


```

