---
title: "Precision-Recall Curves"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

This markdown uses results from the sensitivity analyses for all trials and creates Precision-Recall (P-R) results and plots (for Figure 1).

```{r}
library(PRROC)
library(tidyverse)
library(fishualize)

```

# 1a. Load the classification results of sensitivity analysis and parameters

```{r}
# Change det_combo according to the detectors used in the sensitivity analysis
iters = 2#100
det_code <- 'ALL' #'ECDW' #'ECCEP' 'DWCEP' 'ECDW' DW EC BP


sa_results <- readRDS(file.path('output', 'sens_an_ALL_results.rds'))# 'sens_an_results_filt.rds'))
sa_params <- readRDS(file.path('output', 'sens_an_ALL_params.rds'))


```

# 1b. If P-R data exists, load it to make plots only

```{r}
# Change det_combo to 1 and det_code accordingly if plotting results from different detector combinations

det_code <- 'ALL' #'ECDW' 'ECCEP' 'DWCEP' 'ECDW'

if (det_combo == 0){
data2plot_pr <- readRDS(file.path('output', 'sens_an_all_pr.rds'))
mean_pr_curves <- readRDS(file.path('output', 'sens_an_means_pr.rds'))
} else {
data2plot_pr <- readRDS(file.path('output', paste0('sens_an_', det_code, '_all_pr.rds')) )
mean_pr_curves <- readRDS(file.path('output', paste0('sens_an_', det_code, '_means_pr.rds')) )
}

```

# 2. Make Precision-Recall dataframe

```{r}
data2plot_pr <- data.frame()

for (y in (1:length(sa_params[["iters"]])) ){ 
  for (z in (1:length(sa_params[["callsPrd"]]))) {
    
# Get true binary labels    
true_labels <- factor(sa_results[[y]][[z]][["pred_results"]][["original"]], levels= c("X33", "X577")) 

# Calculate prevalence ( proportion of the total population that belongs to the positive class, FKWs )
prevalence = sum(true_labels=='X33')/ (sum(true_labels=='X33') +sum(true_labels=='X577'))

# Get model-predicted probabilities for "X33" (positive class)
prob_33 <- sa_results[[y]][[z]][["pred_results"]][["X33"]] 

# Create the PR curve
pr_obj <- pr.curve(scores.class0 = prob_33[true_labels == "X33"],
                   scores.class1 = prob_33[true_labels == "X577"],
                   curve = TRUE)

pr_data <- data.frame(iter = y,
                      tot_sigp = sa_params[["callsPrd"]][z],
                      Recall = pr_obj$curve[,1],
                      Precision = pr_obj$curve[,2],
                      Threshold = pr_obj$curve[,3],
                      AUPRC = pr_obj$auc.integral,
                      prev = prevalence) %>% filter(Recall > 0)


data2plot_pr <- rbind(data2plot_pr, pr_data)
  }
}

```

# 3. Calculate mean P-R curves for all signal levels

```{r}
# Define common recall points for interpolating the mean curves
recall_points <- seq(0, 1, length.out = 100)

# Calculate the mean curve coordinates per tot_sigp
mean_pr_curves <- data2plot_pr %>%
  # Group by the model to perform interpolation separately
  group_by(tot_sigp, iter) %>%
  do({
    # Interpolate Precision values at common Recall points
    approx_precision <- approx(.$Recall, .$Precision, xout = recall_points, rule = 2)
    data.frame(Recall = approx_precision$x, Precision = approx_precision$y, Model = unique(.$tot_sigp))
  }) %>%
  ungroup() %>%
  # Now group by the common Recall points and find the mean Precision across models
  group_by(tot_sigp, Recall) %>%
  summarise(Mean_Precision = mean(Precision, na.rm = TRUE), .groups = 'drop')

```

## 3b. Calculate F1-Score

```{r}
mean_pr_curves$f1 <- 2 * mean_pr_curves$Mean_Precision * mean_pr_curves$Recall / (mean_pr_curves$Mean_Precision+mean_pr_curves$Recall)

f1_pt <- mean_pr_curves[which.max(mean_pr_curves$f1), ] 
```

## Save P-R Data

```{r}

saveRDS(data2plot_pr, file.path('output', paste0('sens_an_', det_code, '_total_pr.rds')))
  
  saveRDS(mean_pr_curves, file.path('output', paste0('sens_an_', det_code, '_means_pr.rds')) )


```

# 4. Plot all P-R curves

Plots all P-R curves for all iterations.

```{r}
multi_pr_plot <- ggplot(data2plot_pr, aes(x = Recall, y = Precision)) +
  
  # Plot individual model curves (colored by total signals)
  # interaction() prevents sawtooth, ensures that the correct points are connected between both factors
  geom_line(aes(color = as.factor(tot_sigp), group = interaction(tot_sigp, iter)), 
            linewidth = 0.8, alpha = 0.8) +
  
  # Plot the averaged curve (bold and black)
  geom_line(data = mean_pr_curves,
            aes(y = Mean_Precision, group = as.factor(tot_sigp)),
            color = 'red', 
            linewidth = 0.75, linetype = "dashed") +
  # Add baseline prevalence line
  geom_hline(yintercept = mean(data2plot_pr$prev), linetype = "dotted", linewidth=1.2, color = "darkgray") +
  
  labs(title = "Precision-Recall Curves (with Averaged Curves)",
       subtitle = paste("Includes", length(iters), "runs. Baseline Prevalence:", round(prevalence,3) ),
       x = "Recall (Sensitivity)",
       y = "Precision",
       color = "Signals per Detector") +
  scale_colour_viridis_d() +
  # scale_color_manual(values = c("Model A" = "#0072B2", "Model B" = "#D55E00")) +
  theme_bw() +
  coord_fixed() +
  xlim(0, 1) + ylim(0, 1)

multi_pr_plot
```

## Save Plot

```{r}
# Saves using filenames based on detectors that are included

ggsave( file= file.path('output', paste0('pr_curves_', det_code, '_total.png') ), plot = multi_pr_plot, width = 10, height = 6, dpi = 300 ) 


```

# 5. Plot mean P-R curves only
Plot only the mean P-R curve for each signal per detector level
Change plot title according to the type of detectors included
```{r}
multi_pr_plot_mean <- ggplot() +
  geom_line(data = mean_pr_curves,
            aes(x = Recall, y = Mean_Precision, group = as.factor(tot_sigp),
            color = as.factor(tot_sigp)),
            linewidth = 1) +
  # Add baseline prevalence line
  geom_hline(yintercept = mean(data2plot_pr$prev), linetype = "dotted", linewidth=1.2, color = "darkgray") +
  
  # Add F1 score
  # geom_point(data=f1_pt,
  #            aes(x=Recall, y=Mean_Precision),
  #            color = 'red') +
  
  labs(
     title = "a) All Signal Types",
        # "b) Whistles",
       # "b) Clicks & Whistles",
    #"a) Whistles & Burst Pulses",
       x = "Recall (Sensitivity)",
       y = "Precision",
       color = "Signals per Detector") +
  scale_color_fish_d(option = "Scarus_quoyi") +
  # scale_colour_viridis_d() +
  # scale_color_manual(values = c("Model A" = "#0072B2", "Model B" = "#D55E00")) +
  theme_bw() +
  
  theme(plot.title = element_text(size = 20),
        axis.title = element_text(size = 17),
        axis.text = element_text(size = 15),
        legend.text = element_text(size = 12),
        legend.title = element_text(size=14)) + #, face = "bold")) +
  
  coord_fixed() +
  xlim(0, 1) + ylim(0, 1)

multi_pr_plot_mean
```

## Save Plot to Manuscript folder

```{r}

ggsave( file= file.path('output', 'figures', paste0('pr_curves_', det_code, '_means.png') ), plot = multi_pr_plot_mean, width = 10, height = 6, dpi = 300 ) 


```

# 6. Find Optimal Threshold

```{r}
target_recall <- 0.75
target_precision <- 0.80


# 3. CALCULATE DISTANCE TO TARGET
# We calculate the Euclidean distance (d = sqrt((P_actual - P_target)^2 + (R_actual - R_target)^2))
# The point with the smallest distance is the closest match to the target.
data2plot_pr <- data2plot_pr %>%
  mutate(
    # Calculate the squared difference from the target for both metrics
    distance_sq = (Precision - target_precision)^2 + (Recall - target_recall)^2
  ) 

# 4. FIND THE OPTIMAL THRESHOLD
optimal_row <- data2plot_pr %>%
  arrange(distance_sq) %>% head(1)

# Get the coordinates of the optimal point on the average curve by calculating the squared difference from the target for both metrics
optimal_avg_point <- mean_pr_curves %>%
    mutate(distance_sq = (Mean_Precision - target_precision)^2 + (Recall - target_recall)^2
  ) %>% arrange(distance_sq) %>% head(1)


```

