---
title: 'BANTER_Predict: Plots and Tables'
author: "Yvonne Barkley"
date: "2025-08-04"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Libraries and settings

```{r}
#Load libraries
library(PAMpal)
library(dplyr)
library(manipulate)
library(banter)
library(randomForest)
library(readr)
library(tidyverse)
library(here)
library(patchwork)

#Set time zone to UTC
Sys.setenv(TZ = 'UTC')
```

## Load dataframe with all events, signal counts, BANTER scores, 
VVAO refers to Pc events only, so changed column name to specify that.


```{r}
# Case study data only: 2017, 2023, 2024
all_sigs <- read.csv(here('output', paste0('case_studies_all_data_2026-03-11.csv'))) 
# csv created in 04_results_table1.qmd

  
#   read_csv(file = file.path( 'Output', 'AllSignals_CaseStudies_20251217.csv'), col_types = cols(event.id = col_character(), VVAO = col_character()))
# 
# # csv with only Pc banter scores of filtered events
# bant_pc <- read_csv(file = file.path( 'Output', 'AllScores_Pc.csv'), col_types = cols(event.id = col_character()) ) %>% 
#   select(event.id:year)

# bant_pc <- read_csv(file = file.path( 'Output', 'AllScores_SApreds_Pc.csv'), col_types = cols(event.id = col_character()) )

```

# METHODS: Plots

## Density plots for SSF
Includes data from 2018-2024 surveys, using only visually-verified Pc events
```{r}
allClicks_vv <- readRDS(file.path('data/fig1_ssf_densityplot_rawpeaks.rds'))
allWhistles_vv <- readRDS(file.path('data/fig1_ssf_densityplot_rawwhistles.rds'))


# Remove 1705108 due to snapping shrimp contaminating the data
data_ssf <- filter(allClicks_vv, eventId != "1705108") 
p90 <- round(quantile(data_ssf$peak, 0.88, na.rm = TRUE), 2)

fig1a <- ggplot() +
  # geom_density(aes(data_ssf$peak),fill="#fde0dd", color="#fcc5c0", alpha=1) + #25th percentile of peak frequency
  geom_density(aes(data_ssf$peak),fill="#dadaeb", color="#9e9ac8", alpha=1) + #75th percentile of peak frequency
  # geom_density(aes(data_ssf$click_medPeakFreq_kHz),fill="#c51b8a", color="#7a0177", alpha=0.5) + #median peak frequency
  xlim(1,max(data_ssf$peak))+
  ylim(0,0.1)+
geom_vline(xintercept = p90, linetype = "dashed", color = "#c51b8a", size = 0.7) +
  annotate("text", x = p90, y = 0.02, label = paste(p90, ' kHz cut-off'), 
           hjust = -0.09, vjust = -1, color = "#c51b8a") +
  labs(title = 'a) Clicks - Peak Freq.', 
      x = "Frequency (kHz)",
      y = "Density") +
  theme_bw() +
  theme(plot.title = element_text(size = 12),
        axis.title = element_text(size = 11),
        axis.text = element_text(size = 10))

#whistles - median beginning frequency
evWhistleSumm_vv <- allWhistles_vv %>%
  group_by(eventId) %>%
  summarise(
    numWhistles = n(),
    # whistle_medCenterFreq_Hz = median(freqCenter, na.rm = TRUE),
    # whistle_medMedFreq_Hz = median(freqMedian, na.rm = TRUE),
    whistle_medBeginFreq_Hz = median(freqBeg, na.rm = TRUE),
    whistle_percBeginFreq4to8kHz = sum(freqBeg >= 4000 & freqBeg <= 8000)/n())


ggplot(evWhistleSumm_vv, aes(x=eventId, y=freqBeg)) +
  geom_boxplot() +
  scale_y_continuous(
    breaks = seq(0, 30000, by = 2000), 
    limits = c(0, 30000),             # Ensures the axis stays in this range
    expand = c(0, 0)                  # Removes the "floating" gap at the bottom
  )
  

fig1b <- ggplot(evWhistleSumm_vv, aes(x=whistle_medBeginFreq_Hz/1000)) +
  geom_density(fill="#99d8c9", color="#2ca25f", alpha=0.6) +
  xlim(5,8.2) +
  ylim(0,1) +
   labs(title = 'b) Whistles - Median Beg. Freq.', 
      x = "Frequency (kHz)",
      y = "") +
  geom_vline(xintercept = p90, linetype = "dashed", color = "#c51b8a", size = 0.7) +
  annotate("text", x = p90, y = 0.02, label = paste(8250, ' kHz cut-off'), 
           hjust = -0.09, vjust = -1, color = "#c51b8a") +
  theme_bw() +
    theme(plot.title = element_text(size = 12),
        axis.title = element_text(size = 11),
        axis.text = element_text(size = 10))

#whistles - proportion of beginning frequencies between 4-8 kHz

fig1c <- ggplot(evWhistleSumm_vv, aes(x=whistle_percBeginFreq4to8kHz)) +
  geom_density(fill="#74a9cf", color="#034e7b", alpha=0.8)+
  xlim(0.4,1.1)+
  ylim(0,4)+
  labs(title = 'c) Whistles - Proportion with 4-8 kHz', 
      x = "Proportion",
      y = "") +
  theme_bw() +
  theme(plot.title = element_text(size = 12),
        axis.title = element_text(size = 11),
        axis.text = element_text(size = 10)) 


fig1 <- fig1a + fig1b + fig1c + plot_layout(ncol = 3, widths = c(1,1,1))



```
```{r}
ggsave(filename = file.path('manuscript', 'figures', "Fig1_SSF_DensityPlots.jpg"), width = 8, height = 6, dpi = 300, fig1)

```



# RESULTS: Plots

## Mirror Barplot - Fig. 3
Plotting the results of filtering data through the workflow with different classification thresholds.

```{r}
#Load dataframe

# data_tot2 <- read_csv(file.path('data', 'BANTER_Pseudoca_Table1_data.csv'), col_types = cols(class_thld = col_factor(), step = col_factor()))
data_tot$step2 <- factor(
  data_tot$step,
  levels = c("baseline", "MDF", "SSF", "both"),
  labels = c("Unfiltered", "MDF", "SSF", "MDF & SSF")
)

# Create negative mirrored column
data_tot$mirror_bottom <- -data_tot$toss_bott

blue_colors <- c(
  "0.9"  = "#034fdd",  # base blue 
  "0.8"  = "#4586ff",  # lighter blue
  "0.7"  = "#7BAAFF",  # lighter blue
  "0.6"  = "#A2C7FF",  # lightest blue
  "0.5"  = "#bfcfeb")

# gray_colors <- c(
#   "0.9"  = "#353535",   
#   "0.8"  = "#4D4D4D",  
#   "0.7"  = "#606060",  
#   "0.6"  = "#8c8c8c",  
#   "0.5"  = "#c4c4c4")


mirror_bar <- ggplot(data_tot) +
  # Positive bars (top) colored by top_colors
  geom_bar(
    aes(x = step2, y = keep_top, fill = threshold),
    stat = "identity", position = position_dodge(width = 0.9)
  ) +
  
  # Negative bars (bottom) colored by bottom_colors
  geom_bar(
    aes(x = step2, y = mirror_bottom, fill = threshold),
    stat = "identity", position = position_dodge(width = 0.9)
  ) +
  scale_fill_manual(
    values = blue_colors,
    name = "Classification\nThreshold"
    # guide = "none"  # hide duplicate legend
  ) +
  # Show absolute values on y-axis
  scale_y_continuous(
    labels = abs,
    limits = c(-max(data_tot$keep_top), max(data_tot$keep_top))
  ) +
  labs(
    x = "",
    y = "Number of Acoustic Events"
  ) +
  geom_hline(yintercept = 0, color = "#ffd600", linewidth = 0.8) +
  theme_minimal(base_size = 14) +
  theme(
    # axis.title.y = element_text(size = 16, margin = margin(r = 10)),
    axis.text.y  = element_text(size = 12),
    axis.text.x  = element_text(size = 12),
    axis.title.y = element_text(size = 14),# margin = margin(r = 10)),
    legend.title = element_text(size = 12),
    legend.text  = element_text(size = 10)
  )


mirror_bar

  
  
```

```{r}
ggsave(filename = file.path('manuscript', 'figures', "Fig3_mirrorbarplot_blue_newaxis.jpg"), width = 8, height = 6, dpi = 300)

```


## Bubble Plot-Fig 4. PC Banter Scores
Examine events classified as Pc
```{r pc_true}

# Includes all 58 true Pc events, vis-ver and ac-only
pc_true <- scan(text = '1706044 1706298
1706081
1706091
1706007
1706101
1706281
1706269
1706295
1706127
1706132
1706256
1706338
1706258
1706065
1706120
1706257
1706303
1705416
1705109
1705307
1705308
1705108
1705385
1705280
1705075
1705276
1705279
1705016
1705067
1705210
1705292
1705214
1705142
2303309
2303056
2303155
2303356
2303178
2303362
2303130
2303337
2303324
2303275
2303172
2303343
2303210
2401104
2404021
2404091
2404128
2404018
2404126
2404070
2404105
2404121
2404057
2404013'
)
```

```{r}
event_data <- all_sigs %>%
  filter(event.id %in% pc_true) %>% 
  mutate(
    has_clicks = as.logical(numClicks),
    has_whistles = as.logical(numWhistles),
    has_cepstrum = as.logical(NCep),
    sig_combo = case_when(
      has_clicks & has_whistles & has_cepstrum ~ "All Signal Types",
      has_clicks & has_whistles & !has_cepstrum ~ "Clicks & Whistles",
      has_clicks & !has_whistles & has_cepstrum ~ "Clicks & Burst Pulses",
      !has_clicks & has_whistles & has_cepstrum ~ "Whistles & Burst Pulses",
      has_clicks ~ "Clicks",
      has_whistles ~ "Whistles",
      has_cepstrum ~ "Cepstrum",
      TRUE ~ "No Signals"), # The TRUE condition acts as the final 'else'
     event_type = case_when(
      pc_vis == 1 & pc_ac == 1 ~ "Visually-Verified", # Change label as needed
      TRUE ~ "Acoustic-Only"
      ))  #%>%
    # as.factor()
  # )
# data corrections
event_data$sp_id <- ifelse(event_data$sp_id == 36, 377, event_data$sp_id ) #fixing 2404018, Gm Ac-only 377
event_data$sp_id <- ifelse(event_data$sp_id == 2, 377, event_data$sp_id ) #fixing 1705210, Pc acoustics only before turning for Spotters

event_data$is_unid <- grepl("77", event_data$sp_id)


# write.csv(event_data, file.path('Output', 'Fig4_bubbleplot_data.csv'), row.names = F)




fig4_draft <- ggplot(data = event_data, aes(x= sig_combo, y = X33, fill= factor(event_type), size = TS) ) + #, shape = is_unid) ) +
  # geom_point(aes(shape = is_unid), size = 3) +
  geom_jitter( alpha=0.6, 
               stroke=0.8, 
               color = "black", 
               width = 0.2, height=0,
               shape = 21) + 
  
  labs(
    # title = "Progression of Acoustic Events Through Automated Workflow",
    x = "",
    y = "Classification Score",
    fill = "Event Type"
  ) +
  #   scale_shape_manual(
  #   values = c("FALSE" = 21, "TRUE" = 24),
  #   labels = c("FALSE" = "Identified", "TRUE" = "Unidentified"),
  #   name = "Event ID Status"
  # ) +
  scale_fill_manual(values = c("Visually-Verified" = "#7BAAFF",
                               "Acoustic-Only" = "#FF7256")) + 
                               # "2024" = "#1CC225")) +
  # scale_size_binned(range = c(1, 10), n.breaks = 5)+
  scale_size_continuous(range = c(2, 50), name="Total Signals",
                        breaks = c(10, 1e2, 1e3, 5e3, 1e4, 5e4, 1e5)) +
  theme_minimal() +
  theme(legend.position = "right",
        axis.title.y = element_text(size = 25, margin= margin(r=10)),
        axis.title.x = element_text(size = 20),
        axis.text.y = element_text(size = 20),
        axis.text.x = element_text(size = 25, angle=45, vjust=0.9, hjust = 0.9),
        legend.text = element_text(size = 20),  # Increases "Visually-Verified" etc.
    legend.title = element_text(size = 18)) + # Increases "Event Type") +
  guides(
    color = 'none', #guide_legend(override.aes = list(size = 5)),
    fill = guide_legend(override.aes = list(size = 12, alpha=1)))
```

### save bubble plot
```{r}

ggsave(filename = file.path('manuscript', 'figures', "Fig4_bubbleplot.jpg"), plot= fig4, width = 16, height = 14, dpi = 300)

ggsave(filename = file.path('manuscript', 'figures', "Fig4_bubbleplot_draft.jpg"), plot= fig4_draft, width = 16, height = 14, dpi = 300)
```




# GRAVEYARD
## Violin Plot - Fig. 3a
Doesn't show the distribution very well unless using log10 scale. Tried ylim to see how well any distribution can show up with a limited data range. Up to 200ish?
```{r}
plot_violin <- ggplot(all_sigs, aes(x = factor(year), y = TS, fill=factor(year))) +
  geom_violin(position=position_dodge(), alpha = 0.9) +
  geom_jitter(position = position_jitterdodge(jitter.width = 0.8, dodge.width = 1), 
              alpha = 0.5)+
              # aes(color = factor(year))) +
   scale_fill_manual(values = c("2017" = "#7BAAFF", "2023" = "#F577A6", "2024" = "#1CC225")) +
  # scale_color_manual(values = c("2017" = "#7BAAFF", "2023" = "#F577A6", "2024" = "#1CC225")) +
  scale_y_log10(
  breaks = c(10, 100, 1000, 10000, 200000),
  labels = scales::comma#label_comma()
  ) +
  facet_grid(~ interaction(survey, year), scales = "free_x") +
  labs(
    x = "",
    y = "Total Signals per Acoustic Event"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_blank(),  # removes facet strip labels
    legend.position = "none",
    axis.title.y = element_text(size = 16, margin= margin(r=10)),
        axis.title.x = element_text(size = 16),
        axis.text.y = element_text(size = 14),
    axis.text.x = element_text(size = 14),
    text = element_text(face = "bold"))

ggsave(filename = file.path('Plots', "plot_violin_signal_counts.jpg"), width = 10, height = 6, dpi = 300)
```


## Barplot - Fig. 3b
Plotting the results of filtering data through the workflow

```{r}
custom_colors <- c(
  "2017_Total"      = "#7BAAFF",  # base blue
  "2017_Reduced"   = "#A2C7FF",  # lighter blue
  "2017_Pc" = "#C7DCFF",  # lightest blue
  "2023_Total"      = "#F577A6",  # base pink
  "2023_Reduced"   = "#F79ABD",  # lighter pink
  "2023_Pc" = "#FAC0D5",  # lightest pink
  "2024_Total"      = "#1CC225",  # base green
  "2024_Reduced"   = "#60D56A",  # lighter green
  "2024_Pc" = "#A2E6AB"   # lightest green
)

# Make dataset for plotting table values
barplt_df <- data.frame(
  Year = c(2017, 2017, 2017, 2023, 2023, 2023, 2024, 2024, 2024),
  Type = rep(c("Total", "Reduced", "Pc"), 3),
  Count = c(555, 110, 33, 388, 67, 14, 122, 35, 10),
  VA = c("", "", "(21,12)", "", "","(5, 9)", "", "", "(4, 6)")
)

barplt_df$Type <- factor(barplt_df$Type, levels = c("Total", "Reduced", "Pc"))

barplt_df$fill_key <- paste(barplt_df$Year, barplt_df$Type, sep = "_")
barplt_df$fill_key <- factor(barplt_df$fill_key, levels = c("2017_Total", "2017_Reduced", "2017_Pc" , "2023_Total" , "2023_Reduced", "2023_Pc", "2024_Total", "2024_Reduced", "2024_Pc"))


plot_bar <- ggplot(barplt_df, aes(x = factor(Year), y = Count, fill = fill_key)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_fill_manual(values = custom_colors) + #c("Total" = "#7BAAFF", "Reduced" = "#F577A6", "Classified" = "#1CC225")) +
  labs(
    # title = "Progression of Acoustic Events Through Automated Workflow",
    x = "",
    y = "Number of Acoustic Events",
    fill = "Event Type"
  ) +
    #event type label
    geom_text(
    aes(label = Type),
    position = position_dodge(width = 0.9),
    vjust = -1.7,
    # hjust = 0.5,
    size = 4
    ) +
  #count label
   geom_text(
    aes(label = paste0(Count)),
    position = position_dodge(width = 0.9),
    vjust = -0.3,
    size = 3.5
  ) +
  theme_minimal(base_size = 14) + ylim(0,600) +
  theme(legend.position = "",
        axis.title.y = element_text(size = 16, margin= margin(r=10)),
        axis.title.x = element_text(size = 16),
        axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size = 14), 
        text = element_text(face = "bold"))

ggsave(filename = file.path('Plots', "plot_barplot_acevents_comparison.jpg"), width = 8, height = 6, dpi = 300)

```

### Combine plot and x-label ####
```{r}
require(cowplot)
x_label <- ggdraw() + draw_label("Survey Year", fontface = 'bold', size=16)
combo_plot <- plot_grid(plot_violin, NULL, plot_bar, nrow=1, rel_widths = c(1, 0.2, 1))

fig2 <- plot_grid(combo_plot, x_label, nrow=2, rel_heights = c(1, 0.05))
print(fig2)

ggsave(filename = file.path('Plots', "plot_violin-barplot.jpg"), width = 16, height = 6, dpi = 300)
```


















## Results - Various Metrics
```{r}

sum(event_data$sig_combo == 'All Signal Types')
sum(event_data$sig_combo == 'Clicks/Burst Pulses')
sum(event_data$sig_combo == 'Whistles/Burst Pulses')








# total events by year

all_sigs %>%group_by(year) %>% summarise(yearly_total <- n())

all2024 <- all_sigs %>% filter(year == 2024 & TS > 10)   %>% group_by(sp_id) %>% summarise(yearly_total=n())


unids_all <- all_sigs %>% filter(sp_id %in% c(77, 177, 277, 377)) %>% group_by(year, sp_id) %>% summarise(yearly_total = n())

unids_toPc <- all_sigs %>% filter(sp_id %in% c(77, 177, 277, 377) & X33 >0.5) %>% group_by(year, sp_id) %>% summarise(yearly_total = n())



# how many events were remain AFTER filtering for data quantity, TS > 10?
## Use Selene's filtering from event summs code
all_sigs %>% filter(NClicks > 10 | NWhistle > 10 ) %>% group_by(year) %>% 
  summarise(totsig = n())

# events remaining after applying SSC by year - Fig 3b
bant_pc_sigs <- bant_pc_sigs %>% mutate(sp_id = str_remove(original, "^X"))
  bant_pc_sigs %>% group_by(year) %>% 
  summarise(totsig = n())

## how many unids classified as Pc each year?  NOTE: 2024 is 0 due to checking that the concatenated spectrogram slope is to high.
bant_pc_sigs %>% filter(sp_id %in% c(77, 177, 277, 377)) %>% group_by(year, sp_id) %>% 
  summarise(total_sp = n())
# what is the range of scores for Pc?
bant_pc_sigs %>% filter(sp_id %in% c(77, 177, 277, 377)) %>% 
  summarise(minUnid = min(X33),
            maxUnid = max(X33))

# number of sighted Pc - VVAO_Pc = 2
bant_pc_sigs %>%  group_by(year, VVAO_Pc) %>% 
  summarise(sighted = n())


## Remember, 577s don't matter since they don't all meet the SSC

# # filter for 577 results
# tp577 <- all_sigs %>% filter(sp_id !=33 & X577 > 0.5)
# tp577_year2017 %>% group_by(sp_id) %>% 
#   summarise(total_sp = n())
# 
# # How many UNIDS were classified as Pc?
# unids_to_Pc <- all_sigs %>% filter(sp_id !=33 & X577 < 0.5 & TS >10)
# unids_to_Pc %>% group_by(year, sp_id) %>% 
#   summarise(total_sp = n()) 




```
 




## DONT USE-Histogram
Kept for code example

Doesn't show the distribution very well unless using log10 scale. Tried ylim to see how well any distribution can show up with a limited data range. Up to 200ish?
```{r}
all_sigs_filt <- filter(all_sigs, TS <=50000)
ggplot(all_sigs_filt, aes(x = TS)) +
  geom_histogram(binwidth = 1000, fill = "skyblue", color="darkgray") +
  facet_wrap(~ year, ncol=3, scales = "free_x") +
  labs(
    x = "Total Signals",
    y = "Frequency"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_blank(),  # removes facet strip labels
    legend.position = "none",
    axis.text.x = element_text(angle=45, hjust = 1)
  )



## What if we also plot the 95th percentile of data?
# 95% of the signal counts are less than this, which is 11283.
nine_five <- quantile(all_sigs$TS, probs = 0.95)
all_sigs_filt <- filter(all_sigs, TS <= 50000)

nine_five_yr <- all_sigs %>% group_by(year) %>% 
  summarize(p95 = quantile(TS, probs = 0.95) )
# HISTOGRAM
ggplot(all_sigs_filt, aes(x = TS)) +
  geom_histogram(binwidth = 2000, fill = "skyblue", color="darkgray") +
  facet_wrap(~ year, ncol=3, scales = "free_x") +
    geom_vline(data = nine_five_yr, aes(xintercept = p95), linetype = "dashed", color = "red", size = 0.7) +

  labs(
    x = "Total Signals",
    y = "Frequency"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_blank(),  # removes facet strip labels
    legend.position = "none",
    axis.text.x = element_text(angle=45, hjust = 1)
  )




```

