---
title: "Case Study: Table 1 Results"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---
```{r}
library(tidyverse)
library(here)
```



# Load Data
```{r}
# Load all case study data created from 00_data_wrangle.qmd
# cs_all <- read.csv(here('output', paste0('case_studies_all_data_2026-01-03-raw.csv')))
cs_all <- read.csv(here('output', paste0('case_studies_all_data_2026-03-11.csv')))

#Remove 1706259 due to mixed species
# cs_all <- filter(cs_all, event.id !='1706259')
# 
# # Corrected the pc_vis col
# cs_all <- cs_all %>%
#   mutate(pc_vis2 = ifelse(VVAO == 2, 1, 0)) %>%
# relocate(pc_vis2, .after = pc_vis) %>% 
#   select(-pc_vis) %>% 
#   rename(pc_vis = pc_vis2)
# 
# write.csv(cs_all, here('output', paste0('case_studies_all_data_2026-03-11.csv')), row.names = FALSE)

#Vector with event IDs for original 57 Pc events that passed all filters - 57 events from excel sheet, scan(text='57 event ids')
# pc_evts_57 <- readRDS(here('data', 'original_57_pc.rds'))
# pc_evts_58 <- c(1705323,pc_evts_57) #adding in 1705323 as it passed filters
pc_evts_58 <- readRDS(here('data', 'original_58_pc.rds'))


```

# General Result Metrics
```{r}
# total acoustic events
nrow(cs_all)

# total signals
sum(cs_all$TS)
sum(cs_all$numClicks, na.rm = TRUE)
sum(cs_all$NClicks)
sum(cs_all$NCep)

# total sightings, all species
cs_vv <- filter(cs_all, vis_id < 999)
# total acoustic only events, all species
cs_aconly <- filter(cs_all, vis_id == 999)

# total sightings of Pc = true positives
cs_vv_pc <- filter(cs_all, pc_vis ==1 & pc_ac== 1)
nrow(cs_vv_pc)

# What % of acoustic events were visually verified?
round(nrow(cs_vv)/nrow(cs_all)*100,1)

# What % of acoustic events were not visually verified (acoustic-only)?
cs_ac <- filter(cs_all, pc_vis == 0)
round(nrow(cs_ac)/nrow(cs_all)*100,1)

# total acoustic only Pc - corresponds with localized events
cs_ac_pc <- filter(cs_all, pc_vis == 0 & pc_ac== 1)
nrow(cs_ac_pc)

```



# All Events - Baseline
Now do the steps that I would do with the excel sheets
```{r}

# Gives predicted Pc
base_all_pred_pc <- cs_all %>% filter(X33>=0.5)
base_all_pred_uo <- cs_all %>% filter(X577>0.5)

# Do rows add up? TRUE or FALSE
nrow(cs_all) ==
  nrow(base_all_pred_pc) + nrow(base_all_pred_uo)


base_all_results <- data.frame()

for(i in seq(0.5, 0.9, 0.1)){

  base_all_pred_pc_i <- cs_all %>% filter(X33>=i)
  base_all_pred_pc_j <- cs_all %>% filter(X33>=0.5 & X33<i) #Pc events missed by threshold

# Total predicted as Pc
tab_pc_pred <- nrow(base_all_pred_pc_i)

# True positives- Pc predicted as Pc
tab_pc_tp <- nrow(filter(base_all_pred_pc_i, pc_ac == 1)) #59, correct
tab_pc_tp_j <- nrow(filter(base_all_pred_pc_j, pc_ac == 1))


# False positives- UO predicted as Pc
tab_pc_fp <- nrow(filter(base_all_pred_pc_i, pc_ac == 0)) #76, seems correct, Does fp+tp= 133?

# True negatives- UOs are predicted as UO
tab_pc_tn <- nrow(filter(base_all_pred_uo, pc_ac == 0))

# False negatives- Pc predicted as UO
tab_pc_fn <- nrow(filter(base_all_pred_uo, pc_ac == 1)) + tab_pc_tp_j

base_all_results <- rbind(
    base_all_results,
    data.frame(
      threshold = i,
      pred = tab_pc_pred,
      tp   = tab_pc_tp,
      fp   = tab_pc_fp,
      tn   = tab_pc_tn,
      fn   = tab_pc_fn,
      fpr = tab_pc_fp/(tab_pc_fp+tab_pc_tn),
      fnr = tab_pc_fn/(tab_pc_tp+tab_pc_fn),
      prec=tab_pc_tp/(tab_pc_tp+tab_pc_fp),
      rec = tab_pc_tp/(tab_pc_tp+tab_pc_fn)
    )
  )


}
```

# All Events - MDF & SSF
Now do the steps that I would do with the excel sheets for the filtered events.
```{r}
cs_all_MDFSSF <- filter(cs_all, keep == TRUE ) #| pc_vis == 1 & pc == 1 )

cs_all_tp = filter(cs_all, pc_ac == 1 & X33>=0.5)


# Gives predicted Pc
MDFSSF_all_pred_pc <- cs_all_MDFSSF %>% filter(X33>=0.5)

### Do some checks ###
# events that did not pass the filters, but were included in the original 58
MDFSSF_missed_evts <- setdiff(pc_evts_58, MDFSSF_all_pred_pc$event.id)
MDFSSF_missed_evts <- setdiff(MDFSSF_all_pred_pc$event.id, pc_evts_58)
MDFSSF_missed <- filter(cs_all, event.id %in% MDFSSF_missed_evts)

# events that passed the filters, but were not included in original 58
MDFSSF_missed_evts2 <- setdiff(MDFSSF_all_pred_pc$event.id, pc_evts_58)
MDFSSF_missed2 <- filter(cs_all, event.id %in% MDFSSF_missed_evts2)

# UOs that passed the filters
MDFSSF_all_pred_uo <- cs_all_MDFSSF %>% filter(X577>0.5)

# Do rows add up? TRUE or FALSE
nrow(cs_all_MDFSSF) ==
  nrow(MDFSSF_all_pred_pc) + nrow(MDFSSF_all_pred_uo)

 #+ tab_pc_tp_j


MDFSSF_all_results <- data.frame()

for(i in seq(0.5, 0.9, 0.1)){

MDFSSF_all_pred_pc_i <- cs_all_MDFSSF %>% filter(X33>=i)
MDFSSF_all_pred_pc_j <- cs_all_MDFSSF %>% filter(X33>=0.5 & X33<i) #events below threshold

# Total predicted as Pc
tab_pc_pred <- nrow(MDFSSF_all_pred_pc_i)

# True positives- Pc predicted as Pc
tab_pc_tp <- nrow(filter(MDFSSF_all_pred_pc_i, pc_ac == 1)) #57, correct
tab_pc_tp_j <- nrow(filter(MDFSSF_all_pred_pc_j, pc_ac == 1)) #TPs that are below i


# False positives- UO predicted as Pc
tab_pc_fp <- nrow(filter(MDFSSF_all_pred_pc_i, pc_ac == 0)) #76, seems correct, adds up to 133

# True negatives- UOs are predicted as UO
tab_pc_tn <- nrow(filter(MDFSSF_all_pred_uo, pc_ac == 0))

# False negatives- Pc predicted as UO
tab_pc_fn <- nrow(filter(cs_all, keep==FALSE & pc_ac==1 | pc_vis==1 & pc_ac ==1 & X33<0.5)) + tab_pc_tp_j

# tab_pc_fn <-(nrow(cs_all_tp) - tab_pc_tp) + (nrow(filter(MDFSSF_all_pred_uo, pc == 1))) #+ tab_pc_tp_j

# tab_pc_fn2 <- 4 + nrow(filter(MDFSSF_all_pred_uo, pc_ac == 1)) + tab_pc_tp_j


MDFSSF_all_results <- rbind(
    MDFSSF_all_results,
    data.frame(
      threshold = i,
      pred = tab_pc_pred,
      tp   = tab_pc_tp,
      fp   = tab_pc_fp,
      tn   = tab_pc_tn,
      fn   = tab_pc_fn,
      # fn_4removed = tab_pc_fn2,
      fpr = tab_pc_fp/(tab_pc_fp+tab_pc_tn),
      fnr = tab_pc_fn/(tab_pc_tp+tab_pc_fn),
      # fnr_4removed = tab_pc_fn2/(tab_pc_tp+tab_pc_fn2),
      prec=tab_pc_tp/(tab_pc_tp+tab_pc_fp),
      rec = tab_pc_tp/(tab_pc_tp+tab_pc_fn)
      # rec_4removed = tab_pc_tp/(tab_pc_tp+tab_pc_fn2)
    )
  )


}
```


## MDF Only (mirror plot)
```{r}
MDF_only <- filter(cs_all, keepMDF == TRUE )
# UOs that passed the filters
MDF_only_pred_uo <- MDF_only %>% filter(X577>0.5)
MDF_only_pred_pc <- MDF_only %>% filter(X33>=0.5)


MDF_only_results <- data.frame()

for(i in seq(0.5, 0.9, 0.1)){

MDF_only_pred_pc_i <- MDF_only %>% filter(X33>=i)
MDF_only_pred_pc_j <- MDF_only %>% filter(X33>=0.5 & X33<i) #events below threshold

# Total predicted as Pc
tab_pc_pred <- nrow(MDF_only_pred_pc_i)

# True positives- Pc predicted as Pc
tab_pc_tp <- nrow(filter(MDF_only_pred_pc_i, pc_ac == 1)) #57, correct
tab_pc_tp_j <- nrow(filter(MDF_only_pred_pc_j, pc_ac == 1)) #TPs that are below i


# False positives- UO predicted as Pc
tab_pc_fp <- nrow(filter(MDF_only_pred_pc_i, pc_ac == 0)) #76, seems correct, adds up to 133

# True negatives- UOs are predicted as UO
tab_pc_tn <- nrow(filter(MDF_only_pred_uo, pc_ac == 0))

# False negatives- Pc predicted as UO
tab_pc_fn <- nrow(filter(cs_all, keep==FALSE & pc_ac==1 | pc_vis==1 & pc_ac ==1 & X33<0.5))  + tab_pc_tp_j
# nrow(filter(MDF_only_pred_uo, pc_ac == 1))

# tab_pc_fn <-(nrow(cs_all_tp) - tab_pc_tp) + (nrow(filter(MDFSSF_all_pred_uo, pc == 1))) #+ tab_pc_tp_j

tab_pc_fn2 <- 4 + nrow(filter(MDF_only_pred_uo, pc_ac == 1)) + tab_pc_tp_j

MDF_only_results <- rbind(
    MDF_only_results,
    data.frame(
      threshold = i,
      pred = tab_pc_pred,
      tp   = tab_pc_tp,
      fp   = tab_pc_fp,
      tn   = tab_pc_tn,
      fn   = tab_pc_fn,
      # fn_4removed = tab_pc_fn2,
      fpr = tab_pc_fp/(tab_pc_fp+tab_pc_tn),
      fnr = tab_pc_fn/(tab_pc_tp+tab_pc_fn),
      # fnr_4removed = tab_pc_fn2/(tab_pc_tp+tab_pc_fn2),
      prec=tab_pc_tp/(tab_pc_tp+tab_pc_fp),
      rec = tab_pc_tp/(tab_pc_tp+tab_pc_fn)
      # rec_4removed = tab_pc_tp/(tab_pc_tp+tab_pc_fn2)
    )
  )


}
```

## SSF Only (mirror plot)
```{r}
SSF_only <- filter(cs_all, keepSSF == TRUE )
# UOs that passed the filters
SSF_only_pred_uo <- SSF_only %>% filter(X577>0.5)

SSF_only_results <- data.frame()

for(i in seq(0.5, 0.9, 0.1)){

SSF_only_pred_pc_i <- SSF_only %>% filter(X33>=i)
SSF_only_pred_pc_j <- SSF_only %>% filter(X33>=0.5 & X33<i) #events below threshold

# Total predicted as Pc
tab_pc_pred <- nrow(SSF_only_pred_pc_i)

# True positives- Pc predicted as Pc
tab_pc_tp <- nrow(filter(SSF_only_pred_pc_i, pc_ac == 1)) #57, correct
tab_pc_tp_j <- nrow(filter(SSF_only_pred_pc_j, pc_ac == 1)) #TPs that are below i


# False positives- UO predicted as Pc
tab_pc_fp <- nrow(filter(SSF_only_pred_pc_i, pc_ac == 0)) #76, seems correct, adds up to 133

# True negatives- UOs are predicted as UO
tab_pc_tn <- nrow(filter(SSF_only_pred_uo, pc_ac == 0))

# False negatives- Pc predicted as UO
tab_pc_fn <- nrow(filter(SSF_only_pred_uo, pc_ac == 1)) + tab_pc_tp_j

# tab_pc_fn <-(nrow(cs_all_tp) - tab_pc_tp) + (nrow(filter(MDFSSF_all_pred_uo, pc == 1))) #+ tab_pc_tp_j

tab_pc_fn2 <- 4 + nrow(filter(SSF_only_pred_uo, pc_ac == 1)) + tab_pc_tp_j

SSF_only_results <- rbind(
    SSF_only_results,
    data.frame(
      threshold = i,
      pred = tab_pc_pred,
      tp   = tab_pc_tp,
      fp   = tab_pc_fp,
      tn   = tab_pc_tn,
      fn   = tab_pc_fn,
      fn_4removed = tab_pc_fn2,
      fpr = tab_pc_fp/(tab_pc_fp+tab_pc_tn),
      fnr = tab_pc_fn/(tab_pc_tp+tab_pc_fn),
      fnr_4removed = tab_pc_fn2/(tab_pc_tp+tab_pc_fn2),
      prec=tab_pc_tp/(tab_pc_tp+tab_pc_fp),
      rec = tab_pc_tp/(tab_pc_tp+tab_pc_fn),
      rec_4removed = tab_pc_tp/(tab_pc_tp+tab_pc_fn2)
    )
  )


}
```


### Mirror-plot prep
```{r}

base_all_results2 <- base_all_results %>% select(threshold, pred) %>% mutate(fill_key = paste0("baseline_", seq(0.5, 0.9, 0.1)), step = 'baseline') 

base_all_results2$keep_top <-  base_all_results2$pred
base_all_results2$toss_bott <-  base_all_results2$pred-base_all_results2$pred


MDFSSF_all_results2 <- MDFSSF_all_results %>% select(threshold, pred) %>% mutate(fill_key = paste0("both_", seq(0.5, 0.9, 0.1)), step = 'both')

MDFSSF_all_results2$keep_top <- MDFSSF_all_results2$pred
MDFSSF_all_results2$toss_bott <- base_all_results2$pred-MDFSSF_all_results2$pred


MDF_only_results2 <- MDF_only_results %>% select(threshold, pred) %>% mutate(fill_key = paste0("MDF_", seq(0.5, 0.9, 0.1)), step = 'MDF')
MDF_only_results2$keep_top <- MDF_only_results2$pred
MDF_only_results2$toss_bott <- base_all_results2$pred-MDF_only_results2$pred


SSF_only_results2 <- SSF_only_results %>% select(threshold, pred) %>% mutate(fill_key = paste0("SSF_", seq(0.5, 0.9, 0.1)), step = 'SSF')
SSF_only_results2$keep_top <- SSF_only_results2$pred
SSF_only_results2$toss_bott <- base_all_results2$pred-SSF_only_results2$pred


data_tot <- rbind(base_all_results2, MDFSSF_all_results2, MDF_only_results2, SSF_only_results2)

data_tot$threshold <- as.factor(data_tot$threshold)

```

# Visually-Verified Events - Baseline
```{r}

# Gives predicted Pc
base_vv_pred_pc <- cs_vv %>% filter(X33>=0.5)
base_vv_pred_uo <- cs_vv %>% filter(X577>0.5)

# Do rows add up? TRUE or FALSE
nrow(cs_vv) ==
  nrow(base_vv_pred_pc) + nrow(base_vv_pred_uo)
# Pc sighting missed by banter
  base_vv_missed <- cs_vv %>% filter(pc_vis==1 & pc_ac ==1 & X33<0.5)
  
  base_vv_missedSSF <- cs_vv %>% filter(pc_vis==1 & pc_ac ==1 & X33>=0.5 & keepSSF == FALSE)
    
  base_vv_missedMDF <- cs_vv %>% filter(pc_vis==1 & pc_ac ==1 & X33>=0.5 & keepMDF == FALSE)


base_vv_results <- data.frame()

for(i in seq(0.5, 0.9, 0.1)){

  base_vv_pred_pc_i <- cs_vv %>% filter(X33>=i)
  base_vv_pred_pc_j <- cs_vv %>% filter(X33>=0.5 & X33<i) #Pc events missed due to higher threshold
  
# Total predicted as Pc
tab_pc_pred <- nrow(base_vv_pred_pc_i)

# True positives- Pc predicted as Pc
tab_pc_tp <- nrow(filter(base_vv_pred_pc_i, pc_ac == 1)) 
tab_pc_tp_j <- nrow(filter(base_vv_pred_pc_j, pc_ac == 1))


# False positives- banter predicted known UOs as Pc
tab_pc_fp <- nrow(filter(base_vv_pred_pc_i, pc_ac == 0)) 

# True negatives- UOs are predicted as UO
tab_pc_tn <- nrow(filter(base_vv_pred_uo, pc_ac == 0 & pc_vis2 == 0))

# False negatives- Pc predicted as UO
tab_pc_fn <- nrow(filter(base_vv_pred_uo, pc_ac == 1)) + tab_pc_tp_j

base_vv_results <- rbind(
    base_vv_results,
    data.frame(
      threshold = i,
      pred = tab_pc_pred,
      tp   = tab_pc_tp,
      fp   = tab_pc_fp,
      tn   = tab_pc_tn,
      fn   = tab_pc_fn,
      fpr = (tab_pc_fp/(tab_pc_fp+tab_pc_tn))*100,
      fnr = (tab_pc_fn/(tab_pc_tp+tab_pc_fn))*100,
      prec=tab_pc_tp/(tab_pc_tp+tab_pc_fp),
      rec = tab_pc_tp/(tab_pc_tp+tab_pc_fn)
    )
  )


}


```


# Vis-Ver - MDF & SSF
Now do the steps that I would do with the excel sheets for the filtered events.
```{r}
cs_vv_MDFSSF <- filter(cs_vv, keep == TRUE)# | pc_vis == 1 & pc == 1 )

# This is the total vis-verified true positives for calculations = 31 sightings
cs_vv_tp = filter(cs_vv, pc_ac== 1 & pc_vis2==1)


# Gives predicted Pc - TP, but toss 4
MDFSSF_vv_pred_pc <- cs_vv_MDFSSF %>% filter(X33 >= 0.5)

# Pc vv tossed by filter(s) and/or BANTER
MDFSSF_vv_missed <- cs_vv %>% filter(keep==FALSE & pc_vis2==1 | pc_vis==1 & pc_ac ==1 & X33<0.5)

# UOs that passed the filters - TN
MDFSSF_vv_pred_uo <- cs_vv_MDFSSF %>% filter(X577>0.5)

# Do rows add up? TRUE or FALSE
nrow(cs_vv_MDFSSF) ==
  nrow(MDFSSF_vv_pred_pc) + nrow(MDFSSF_vv_pred_uo)


MDFSSF_vv_results <- data.frame()

for(i in seq(0.5, 0.9, 0.1)){

MDFSSF_vv_pred_pc_i <- cs_vv_MDFSSF %>% filter(X33>=i)
MDFSSF_vv_pred_pc_j <- cs_vv_MDFSSF %>% filter(X33>=0.5 & X33<i) #events below threshold

# Total predicted as Pc
tab_pc_pred <- nrow(MDFSSF_vv_pred_pc_i)

# True positives- Pc predicted as Pc
tab_pc_tp <- nrow(filter(MDFSSF_vv_pred_pc_i, pc_ac == 1)) #57, correct
tab_pc_tp_j <- nrow(filter(MDFSSF_vv_pred_pc_j, pc_ac == 1)) #TPs that are below i


# False positives- UO predicted as Pc
tab_pc_fp <- nrow(filter(MDFSSF_vv_pred_pc_i, pc_ac == 0)) #76, seems correct, adds up to 133

# True negatives- sightings of UOs are predicted as UO, 
tab_pc_tn <- nrow(filter(MDFSSF_vv_pred_uo, pc_ac == 0))

# False negatives- Here we KNOW Pc predicted as UO
tab_pc_fn <- nrow(filter(cs_vv, keep==FALSE & pc_vis2==1 | pc_vis==1 & pc_ac ==1 & X33<0.5)) + tab_pc_tp_j

# 
# 
# tab_pc_fn2 <- 4 + nrow(filter(MDFSSF_vv_pred_uo, pc_ac == 1)) + tab_pc_tp_j

MDFSSF_vv_results <- rbind(
    MDFSSF_vv_results,
    data.frame(
      threshold = i,
      pred = tab_pc_pred,
      tp   = tab_pc_tp,
      fp   = tab_pc_fp,
      tn   = tab_pc_tn,
      fn   = tab_pc_fn,
      # fn_4removed = tab_pc_fn2,
      fpr = tab_pc_fp/(tab_pc_fp+tab_pc_tn),
      fnr = tab_pc_fn/(tab_pc_tp+tab_pc_fn),
      fnr_4removed = tab_pc_fn2/(tab_pc_tp+tab_pc_fn2),
      prec=tab_pc_tp/(tab_pc_tp+tab_pc_fp),
      rec = tab_pc_tp/(tab_pc_tp+tab_pc_fn),
      # rec_4removed = tab_pc_tp/(tab_pc_tp+tab_pc_fn2)
    )
  )


}
```
