---
title: "Sensitivity Analysis of Prediction Performance for Pseudorca vs Other Species"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

#To Do - Add figure of final model performance from 01\_.qmd

# Prediction Steps

## Load Libraries and settings

```{r}

install_if_missing_and_load <- function(pkg) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg)
    library(pkg, character.only = TRUE)
  }
}

# devtools::install_github('TaikiSan21/PAMpal')
library(PAMpal)
library(tidyverse)
library(here)
library(rfPermute)
library(banter)
library(patchwork)
library(manipulate) #
library(caret) #confusionMatrix
library(foreach)
library(future)
library(doFuture)
library(progressr)

# source(here('code/functions/makeBanterID.r'))
source(here('code/functions/PAMpalWishlist/PAMpalWishlistYB.r'))
source(here('code/functions/predictions.r'))
source(here('code/functions/filterClicks.r'))

#Set time zone to UTC
Sys.setenv(TZ = 'UTC')


## Load BANTER model

bant_model <- readRDS(file.path("notebooks", "bantMDL_HICEAS2017-CH5_Filtered_577_2024-05-20.rds")) #most updated from Selene



## Load acoustic study to predict on
acstudy_predict <- readRDS(file = here('notebooks/TA_AcStudies_HI-MACS_predict.rds') ) 

## species that we do not want to include
drop_Sp <- c('77','177','277','377','49','59','61','65')
```

## Play with banter object

```{r}
# banter_pred <- export_banter( c(events(acstudy_predict), training=FALSE) )

# banter_pred

# bntSummaryTable <- function(x) {
#   bind_rows(lapply(x$detectors, function(y) {
#     tmp <- left_join(y, x$events, by='event.id')
#     select(tmp, event.id, species)
#   }), .id = 'detector') %>% group_by(event.id,species,detector) %>%
#      summarise(Detections = n())
# }



```

## Parameters for Predictions

Set values and save.

```{r}

#TEST PARAMETERS
# For all detectors
callsMod <- 'All' #c(50, 500, 1000, 50000, 107000) #c(50,60,70) #c(round(seq(5, 80, length.out = 10),0))#, seq(55, 1100, by = 100))
callsPrd <- c(round(seq(10, 200, length.out = 1),0), 300, 400, seq(500, 40000, length.out = 1)) #c(10,20,30)

# calls <- round(seq(from = 5, to = 100, length.out = 10),0) #seq(2, 100, 10) #how many calls are needed from each detector? max 5000
# calls <- seq(100, 1000, 100)
# dets <- c(2:4) #which detectors to use?
dets <- c(2:8)

iters <- c(1:2)

predxn_params <- list(callsMod=callsMod,
                     callsPrd=callsPrd,
                     dets=dets,
                     iters=iters,
                     notes = 'FULL MODEL. Excludes BWs and Unids. All detectors. 17 events. Filtered clicks!')
                
saveRDS(predxn_params, file = paste0(here('results/PcVsOther/Sensitivity_analysis'), '/predxnParameters_', Sys.Date(), '.rds'))

```

## Sensitivity Analysis Loop

```{r}

### START LOOP ####

# choose model
  # bant_model <- readRDS( paste0(here('results/PcVsOther/Full_Model'),'/bant_model_rmCF.rds') )
                           
#Model Results
# bantmod_results <- list()     # overall model scores per iteration and signal #
# bantmod_evts  <- list()       # individual event classification per iteration and signal #
# banterModelsList <- list()    # List of full model info per iteration and signal #
# bantpred_results <- list()    # overall predictions per iteration and signal #
# bantpred_confmatAll <- list() # 
# bantpred_confmatScores <- list()
all_callPrds <- list()
counter <-1

options(doFuture.rng.onMisuse = "ignore", future.globals.maxSize = 2 * 1024^3)
plan("multisession", workers=7)

tictoc::tic(

for (i in iters){

      # for (call_prd in callsPrd){
    pred_output <- foreach(p = callsPrd,  .options.future = list(packages = c("banter", "randomForest"))) %dofuture% {

    #The variation in results stems from the random selection 
    #of signals from each detector in an encounter.
    acstudy_predict_sub <- sampleDetector(acstudy_predict, n=p)  
    
    # Print Run Info
    cat("***PREDICTIONS***: Iter", i, "For pred calls=", p, ", mod calls=", callsMod, ", and detectors =", dets)
    
    # banter_pred <- export_banter( c(events(acstudy_predict_sub), training=FALSE) )
    banter_pred <- export_banter(acstudy_predict_sub, training=FALSE, dropSpecies = drop_Sp) 
    
    ## Make a dataframe with event IDs and original species codes
    origSpCodes <- data.frame(banter_pred[["events"]])
    
    banter_pred <- changeBanterSpeciesId(banter_pred, "577")
    
    ### CLICK DETECTOR FILTERS ####
    #Remove clicks with bandwidth at 10dB < 5 kHz (Load 'dplyr' package)
    for(d in c(1,2,3,4,5,8)){  #ensure that detector numbers match here
      banter_pred$detectors[[d]]<-filter(banter_pred$detectors[[d]],BW_10dB > 5)
      banter_pred$detectors[[d]]<-filter(banter_pred$detectors[[d]],peak > 5 & peak < 80)
      banter_pred$detectors[[d]]<-filter(banter_pred$detectors[[d]],duration > 2 & duration < 1000)
    }
    
    #Remove clicks in individual detectors
    banter_pred$detectors$Click_Detector_1<-filter(banter_pred$detectors$Click_Detector_1, peak>2 & peak<15)
    banter_pred$detectors$Click_Detector_2<-filter(banter_pred$detectors$Click_Detector_2, peak>15 & peak<30)
    banter_pred$detectors$Click_Detector_3<-filter(banter_pred$detectors$Click_Detector_3, peak>30 & peak<50)
    banter_pred$detectors$Click_Detector_4<-filter(banter_pred$detectors$Click_Detector_4, peak>30 & peak<50)
    banter_pred$detectors$Click_Detector_5<-filter(banter_pred$detectors$Click_Detector_5, peak>50 & peak<80) 
    
    
    ## Apply model, get predictions, make a dataframe to compare to true event IDs to predictions
    
    pred_results <- banter::predict(bant_model, banter_pred)
    
    pred_resultsDF <- as.data.frame(pred_results[["predict.df"]])
    
    pred_resultsDF <- pred_resultsDF[, c(1, 5, 2:4,6)]
    
    pred_resultsDF <- inner_join(origSpCodes, pred_resultsDF, by = 'event.id')
    
    pred_resultsDF$iter = i
    pred_resultsDF$tot_sigp = p
    pred_resultsDF$tot_sigm = callsMod
    pred_resultsDF$dets = paste(dets, collapse = "")
    
   # return(pred_resultsDF)
   
#     predxns <- predictions(acstudy_predict, callsPrd, callsMod, bant_model, i, dets)
# 
# # SAVE list of dataframes with prediction results to look at misclassifieds later
#   for(h in 1:length(predxns[["bantpred_resultsi"]])){
#     bantpred_results[[length(bantpred_results) + 1]] <- predxns[["bantpred_resultsi"]][[h]]


##  MEMORY saving stuff 
# rm( AcStudy_PcUO_sub, banter_mod)
# gc()

# SAVE confusion matrices in a list

# for(h in 1:length(predxns[["bantpred_confMati"]])){
# bantpred_confmatAll[[length(bantpred_confmatAll) + 1]] <- predxns[["bantpred_confMati"]][[h]]
# }#c(confmat = confMat, dets= paste(dets, collapse = ""), iter=i, tot_signals = call_prd)
# 
# # Save confusion matrix overall scores for plotting
# bantpred_confmatScores[[length(bantpred_confmatScores) + 1]] <- predxns[["bantpred_confMatScoresi"]]


 confMat <- confusionMatrix(factor(pred_resultsDF$predicted),factor(pred_resultsDF$original ), mode = 'everything')

 confMatscore <-data.frame(overall=confMat[["overall"]][[1]],
                     true33 = confMat[["table"]][1],
                     false33 = confMat[["table"]][2],
                     false577 = confMat[["table"]][3],
                     true577 = confMat[["table"]][4],
                     iter = i,
                     tot_sigp = p,
                     tot_sigm = callsMod)
 return(list(
   pred_results = pred_resultsDF, 
   confmat_score = confMatscore))

 } # callsPrd
    
 ## save prediction results
    all_callPrds[[counter]] <- pred_output
     counter <- counter + 1 
    
  } #iteration
)
plan("sequential")

tictoc::toc()
```

## Total SA - SAVE

```{r}

## Model Outputs
# bantmod_resultsDF <- do.call(rbind, bantmod_results)

# bantmod_evtsDF <- do.call(rbind, bantmod_evts)

bantpred_resultsDF <- do.call(rbind, pred_output)

bantpred_confmatScoresDF <- do.call(rbind, bantpred_confmatScores)

## Save Model outputs
# saveRDS( bantmod_resultsDF, paste0(here('results/PcVsOther/Sensitivity_analysis'), '/bantDFall2024_', iters[1], '-', iters[length(iters)], '.rdata') )

# saveRDS(bantmod_evts, file= paste0(here('results/PcVsOther/Sensitivity_analysis/eventPredxnList_'),  iters[1], '-', iters[length(iters)], '.rdata' ) )

# saveRDS(bantmod_evtsDF, file= paste0(here('results/PcVsOther/Sensitivity_analysis/eventPredxnDF_'),  iters[1], '-', iters[length(iters)], '.rdata' ) )


## Prediction Outputs
saveRDS(all_callPrds, file= paste0(here('results/PcVsOther/Sensitivity_analysis'), '/', 'all_callPrds-', Sys.Date(), '.rds'))

saveRDS(bantpred_resultsDF, file= paste0(here('results/PcVsOther/Sensitivity_analysis'), '/PredictionsDF-', Sys.Date(), '.rds'))

saveRDS(bantpred_confmatAll, file= paste0(here('results/PcVsOther/Sensitivity_analysis'), '/ConfMatsList.rds')) 
saveRDS(bantpred_results, file= paste0(here('results/PcVsOther/Sensitivity_analysis'), '/PredictionsList.rds'))
saveRDS(bantpred_confmatScores, file= paste0(here('results/PcVsOther/Sensitivity_analysis'), '/ConfMatsScores4Plots.rds'))
saveRDS(bantpred_confmatScoresDF, file= paste0(here('results/PcVsOther/Sensitivity_analysis'), '/ConfMatsScores4PlotsDF.rds'))
        
        


```

## Total SA - PLOT Predictions

### Pull out scores from each iteration in the results list

```{r}
data2plot <- data.frame()

for (y in iters ){ #(1:100)) {
  for (k in (1:length(callsPrd))) {
  
  tmp <-all_callPrds[[y]][[k]][["confmat_score"]]
   
  data2plot <- rbind(data2plot, tmp)
  
}
}
```

### Assign evenly spaced values

```{r}
# Function to use log10 transformation for plotting
assign_even_sequence_by_unique_values <- function(df, column_name, new_column_name = "Even_Sequence", from = 1, to = 12) {
  # Get the unique values
  unique_vals <- sort(unique(df[[column_name]]))
  
  # Generate new sequence for plotting
  even_seq <- log10(callsPrd) #(c(10, 58, 105, 152, 200, 300, 400, 500, 10375, 20250, 30125, 40000))#seq(from = from, to = to, length.out = length(unique_vals))
  
  # Create a lookup table
  mapping <- setNames(even_seq, unique_vals)
  
  # Map the new values to the dataframe
  df[[new_column_name]] <- mapping[as.character(df[[column_name]])]
  
  return(df)
}

df <- data.frame(tot_sigp = rep(c(10, 58, 105, 152, 200, 300, 400, 500, 10375, 20250, 30125, 40000), times = 100))

data2plot2 <- assign_even_sequence_by_unique_values(data2plot, "tot_sigp", "trans_sigp")

head(data2plot2)
data2plot <- data2plot2


```

## Plot Prediction Results

```{r}

cols =  c("#214DBEFF" ,"#51B4FDFF" ,"#00E3DDFF" ,"#00F293FF" ,"#C6FC3FFF","#FF9B00", "#FF479A")


results_scoredf <- filter(data2plot, tot_sigm=="All")#group == 'Overall')# & iter != 5)

#transform signals
# data2plot$trans_sigp <- custom_trans(data2plot$trans_sigp)

results_scorep <- data2plot %>% group_by(tot_sigp, trans_sigp) %>%
                        summarise(mean = mean(overall),
                                sd = sd(overall),
                                mean_mis = mean(false33),
                                sd_mis = sd(false33))# %>% arrange(as.numeric(iter))


p = ggplot(data = results_scorep, aes(x = trans_sigp, y = mean)) +
  geom_line(lwd = .8) +
  geom_point(size=2) +
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width = .1, linewidth = 1) +
        
  scale_color_manual(values = cols[c(1,3,6)],
                     labels = c("Pc", "Other", "Overall")) +
  # scale_fill_fish(option = "Cirrhilabrus_solorensis", direction = -1, begin = 0, end = .9) +  #try this
  labs(title = paste0("BANTER Predictions: Pc vs Other - Full Model, ", iters[length(iters)], " iterations total") , # Clicks Only
       subtitle = paste0("Model: excludes BWs & Unids,", " trees=2000", " & ", 20000, ", sampsize = 15"), # ':', n_evt[length(n_evt)] ) ,
       x = "Signals per Detector",
       y = "Mean Overall Accuracy",
       color = "Score Type") +

scale_x_continuous(breaks = data2plot$trans_sigp,
labels = data2plot$tot_sigp)  +
    scale_y_continuous(breaks = pretty(data2plot$overall, n=5)) +
  theme_bw() +
  theme(plot.title = element_text(size = 18, face = "bold"),
        plot.subtitle = element_text(size=13),
        axis.title.y = element_text(size = 16, margin= margin(r=10)),
        axis.title.x = element_text(size = 16),
        axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size = 10, angle = 50, vjust = 0.8),
        axis.ticks.length=unit(.25, "cm"),
        panel.grid.minor = element_line(color = "white", linewidth  = 0.5,
                                        linetype = "dotted"))
   
  #   labels = c(round(seq(5, 50, length.out = 10),0), seq(55, 1100, by = 100)) ) +
  # scale_y_continuous(limits = c(range(round(results_score_mean2$mean,0))[1] -5, range(round(results_score_mean2$mean,0))[2]+2 ))  
                     # breaks = seq( range(round(results_score_mean2$mean,0))[1] -5, range(round(results_score_mean2$mean,0))[2]+1, by = 5) )

p
## Save Plot
ggsave( paste0( here('results/PcVsOther/Sensitivity_analysis'), '/PredictionScores-iters', iters[length(iters)], '-sigs', min(callsPrd), "-", max(callsPrd),'-', Sys.Date(),'log10.png'), plot = p, width = 10, height = 6, dpi = 300)
```

### Total SA - PLOT Model

```{r}
results_scorem <- data2plot %>% group_by(tot_sigm) %>%
                        summarise(mean = mean(overall),
                                sd = sd(overall),
                                mean_mis = mean(false33),
                                sd_mis = sd(false33))
```

## Predict Only: Sensitivity Analysis

TO DO: Change the number of signals used in the TEST data for each encounter to be predicted and compare scores.

```{r}


results_predxns  <- list()
ConfMatsList <- list()

### START LOOP ####

for (i in iters){
  for (call_val in calls){
 #    for (j in seq_along(dets) ) { #line 251
 # 
 #     # det_seq  = dets[1:j]
 # 
 #     comb <- combn(dets, j, simplify = FALSE)
 # # 
 # # 
 # # # Loop through each combination of detectors
 #    for (c in comb) {

# DELETE? Comment out if all combinations are included:
      c = dets

# Make acoustic study using number of calls per detector, call_val      
 AcStudy_PcUO_sub <- sampleDetector(acstudy_predict, n=call_val)


 # filterTimeProportion(AcStudy_Pc, prop_start=0, prop_end=0.5)
 
 # Print Run Info
    cat("Iter", i, "For calls =", call_val, "and dets sequence =", c)
 
  
 banter_pred <- export_banter(c(events(AcStudy_PcUO_sub)) )#, dropSpecies =  dropStk)
 
 banter_pred <- changeBanterSpeciesId(banter_pred, "577")
 
# sum(sapply(banter_prop$detectors, nrow))

  ### CLICK DETECTOR FILTERS ####
#Remove clicks with bandwidth at 10dB < 5 kHz (Load 'dplyr' package)
for(d in c(1,2,3,4,5,8)){  #ensure that detector numbers match here
  banter_pred$detectors[[d]]<-filter(banter_pred$detectors[[d]],BW_10dB > 5)
  banter_pred$detectors[[d]]<-filter(banter_pred$detectors[[d]],peak > 5 & peak < 80)
  banter_pred$detectors[[d]]<-filter(banter_pred$detectors[[d]],duration > 2 & duration < 1000)
}

#Remove clicks in individual detectors
banter_pred$detectors$Click_Detector_1<-filter(banter_pred$detectors$Click_Detector_1, peak>2 & peak<15)
banter_pred$detectors$Click_Detector_2<-filter(banter_pred$detectors$Click_Detector_2, peak>15 & peak<30)
banter_pred$detectors$Click_Detector_3<-filter(banter_pred$detectors$Click_Detector_3, peak>30 & peak<50)
banter_pred$detectors$Click_Detector_4<-filter(banter_pred$detectors$Click_Detector_4, peak>30 & peak<50)
banter_pred$detectors$Click_Detector_5<-filter(banter_pred$detectors$Click_Detector_5, peak>50 & peak<80) 


## Apply model

results_pred <- predict(bant.mdlAll, banter_pred)

predDF_newRenamed <- results_pred[["predict.df"]]

predDF_newRenamed <- inner_join(testDataDF, predDF_newRenamed, by = 'event.id')

## confusion matrix

confMat <- confusionMatrix(factor(predDF_newRenamed$predicted), factor(predDF_newRenamed$original ))


#Give model a new name with signal # and iteration
if (i <= 9){
  new_name <- paste0("Predictions_", call_val, 'calls_', paste(c, collapse = ""), '_0', i)

  } else {

  new_name <- paste0("Predictions_", call_val, 'calls_', paste(c, collapse = ""), '_', i)

} 


#save confusion matrices in a list

ConfMatsList[[ paste0(new_name, '.rdata') ]] <- c(confmat = confMat, dets= paste(c, collapse = ""), iter=i, tot_signals = call_val)



# SAVE list of dataframes with prediction results to look at misclassifieds later
results_predxns[[length(results_predxns) + 1]] <- c( predDF_newRenamed, dets= paste(c, collapse = ""), iter=i, tot_signals = call_val )

#  MEMORY saving stuff ####
rm( AcStudy_PcUO_sub, banter_pred)
gc()


     

 }

  
  }
  
saveRDS(ConfMatsList, file= paste0(here('results/PcVsOther/Sensitivity_analysis'), '/ConfMatsList.rds') )     
    


  
gc()

#   # }
#   
# }  
# accuracy to plot
ConfMatsList[[3]][["confmat.overall"]][[1]]
```

## Test Data: Export/Filter

```{r}

testData <- export_banter(acstudy_predict)
testDataDF <- data.frame(testData[["events"]])

for(d in c(1,2,3,4,5,8)){  #ensure that detector numbers match here
  testData$detectors[[d]]<-filter(testData$detectors[[d]],BW_10dB > 5)
  testData$detectors[[d]]<-filter(testData$detectors[[d]],peak > 5 & peak < 80)
  testData$detectors[[d]]<-filter(testData$detectors[[d]],duration > 2 & duration < 1000)
}

#Remove clicks in individual detectors
testData$detectors$Click_Detector_1<-filter(testData$detectors$Click_Detector_1, peak>2 & peak<15)
testData$detectors$Click_Detector_2<-filter(testData$detectors$Click_Detector_2, peak>15 & peak<30)
testData$detectors$Click_Detector_3<-filter(testData$detectors$Click_Detector_3, peak>30 & peak<50)
testData$detectors$Click_Detector_4<-filter(testData$detectors$Click_Detector_4, peak>30 & peak<50)
testData$detectors$Click_Detector_5<-filter(testData$detectors$Click_Detector_5, peak>50 & peak<80)



testDatarenamed <- changeBanterSpeciesId(testData, "577")

```

## Apply model to test data

```{r}

# Original Model
# bant.mdlAll <- bant.mdl

results_pred <- predict(bant.mdlAll, testDatarenamed)

predDF_newRenamed <- results_pred[["predict.df"]]

predDF_newRenamed <- inner_join(testDataDF, predDF_newRenamed, by = 'event.id')

results_Summ <- predDF_newRenamed %>% group_by(species, correct) %>% 
  summarise(total = n())
results_Summ2 <- predDF_newRenamed %>% group_by(correct, species) %>% 
  summarise(total = n())

# predDF_Jen <- results_pred[["predict.df"]]
# predDF_Selene <- results_pred[["predict.df"]]


```

## Confusion matrix

```{r}

#1. Make confusion matrix
confMat <- confusionMatrix(factor(predDF_newRenamed$predicted), factor(predDF_newRenamed$original ))
confMat

# Filter out unids
predDF_noUNIDS <- predDF_newRenamed %>% filter(!species %in% c('77', '177', '277', '377'))

confMat_noUNIDS <- confusionMatrix(factor(predDF_noUNIDS$predicted), factor(predDF_noUNIDS$original ))
confMat_noUNIDS

#2. Get details of predictions
tableSp <- table(Species = predDF_newRenamed$species, Predicted = predDF_newRenamed$predicted )

## no unids
tableSp_noUNIDS <- table(Species = predDF_noUNIDS$species, Predicted = predDF_noUNIDS$predicted )


```
